**The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models**

### 2021-03-08 Manuscripts/Manuscript_AM_v3.Rmd
Work on basis plot

#heatmap of the coefficient
p3<-ggplot(basis_plot,aes(x=Basis,y=Basis,fill=cof))+
  geom_tile(aes(color='black'),size=2,show.legend = FALSE)+
  geom_tile(size=2)+
  scale_fill_gradient(low = "white", high = "red")+ 
  geom_text(aes(label=round(cof,1)))+
  theme_classic()

>>>>

#heatmap of the coefficient
p3<-ggplot(basis_plot,aes(x=Basis,y=Basis,fill=cof))+
  geom_tile(aes(color='black'),size=2,show.legend = FALSE)+
  geom_tile(size=2)+
  scale_fill_gradient(low = "white", high = "red")+ 
  geom_text(aes(label=round(cof,2)))+
  theme_classic()
